Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-23 paper.tex
revision 6.4

\subsection{Experimental Results}
The following tests were executed on 2 sets of nodes interconnected by a 1Gb Ethernet network.

The first set, in charge of providing the cloud environment,
consisted of 3 nodes, each equipped with an Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667 MHz.
To deploy an infrastructure as a cloud service, we used OpenStack Icehouse version and QEMU/KVM 0.12.1 as the hypervisors.
A fully-featured OpenStack deployment requires at least three nodes: one controller node that manages the compute nodes 
where the VMs are hosted, one network node that manages the logic
virtual network for the VMs, and one or more compute nodes that 
run the hypervisor and virtual machines.

The second set, composed by 4 nodes, were auxiliary servers with a Tesla C1060 GPU each one. 
Their system operates a Centos 6.6; and the GPUs use CUDA 6.5. 
The GPU virtualization support is based on rCUDA v5.0.

@@

The researchers were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.

>>>>

\subsection{Experimental Results}
The following tests were executed on 2 sets of nodes interconnected by a 1Gb Ethernet network.
All the nodes were equipped with an Intel Xeon E7420 quadcore processor at 2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667 MHz.

The first set, in charge of providing the cloud environment,
consisted of 3 nodes.
To deploy an infrastructure as a cloud service, we used OpenStack Icehouse version and QEMU/KVM 0.12.1 as the hypervisor.
A fully-featured OpenStack deployment requires at least three nodes: a controller node manages the compute nodes 
where the VMs are hosted, a network node that manages the logic virtual network for the VMs, and one or more compute nodes that 
run the hypervisor and VMs.

The second set, composed of 4 nodes, were auxiliary servers with a Tesla C1060 GPU each one. 
The OS was a Centos 6.6; and the GPUs used CUDA 6.5. 
The GPU virtualization support was based on rCUDA v5.0.

@@

This research was supported by Universitat Jaume I research project (P11B2013-21); and projects
TIN2014-53495-R from MINECO and FEDER.
